Addressing climate change and development pressures in an urban estuary through habitat restoration planning

### 2022-08-23 manu-draft.qmd
target table added, tables done

```{r, results = 'hide'}
library(knitr)
library(here)
library(flextable)
library(dplyr)
library(officer)
library(officedown)

load(file = here('tabs/subttab.RData'))
load(file = here('tabs/acretab.RData'))
```

@@

@@

Table 3: Summary of the opportunity assessment analysis

Table 4: Targets

>>>>

```{r, results = 'hide'}
library(knitr)
library(here)
library(flextable)
library(dplyr)

load(file = here('tabs/subttab.RData'))
load(file = here('tabs/acretab.RData'))
load(file = here('tabs/currtab.RData'))
load(file = here('tabs/targtab.RData'))
```

@@

\newpage

@@

\newpage

```{r}
#| tbl-cap: Summary of habitat restoration opportunities in the Tampa Bay watershed.  Summaries are based on 2017 land use data, 2018 subtidal data, best estimates for habitat types not in existing GIS layers, and current extent of existing and proposed conservation lands.
currtab
```

\newpage

```{r}
#| tbl-cap: Recommended 2030 targets and 2050 goals for habitat restoration and protection in the Tampa Bay watershed. Targets and goals are based on 2017 land use data, 2018 subtidal data, best estimates for habitat types not in existing GIS layers, and current extent of existing and proposed conservation lands.
targtab
```

\newpage
